---
title: "Rworksheet#2_Sante"
author: "Sharrene Sante"
date: "2023-11-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1. Generate a sequence form -5 to 5.
```{r num1a}
#output: [1] 1 2 3 4 5 6 7 8 9 10 11
#If I use the : operator, the output will be 1 to 11 , but if I change :
sequence <- seq(-5:5)
sequence
```
```{r num1b}
#b. What will be the value of x?
#Value of x will be a sequence from 1 to 7
x <- 1:7
x
```
```{r num2}
#2. Create a vector using seq() function.
#output: [1] 1.0 1.2 1.4 1.6 1.8 2.0 2.2 2.4 2.6 2.8 3.0
# The numbers are sequence but in 0.2 interval.
seq(1, 3, by=0.2)
```

#3. Create a vector with the age of the factory workers.
```{r num3a}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
         22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35,
         24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26,
         18)

#a. Access the 3rd element. The third value is 22.
element_3 <- age[3]
element_3
```
```{r num3b}
#b. Access 2nd and 4th element. The second element is 28 while the fourth element is 36.

element_2 <- age[2]
element_4 <- age[4]
element_2
element_4
```
```{r num3c}
#c. Access all but the 4th and 12th element is not included.
# Element 4 is 36 while element 12 is 31.
new_age <- age[4]
new_age
new_age2 <- age[12]
new_age2
```

#4. Create a vector then named the vector, names (x)
```{r num4}
#output: first second third
#          3     0      9
names <- c("first"=3, "second"=0, "third"=9)
names

#output: first third
#          3     9
names[c("first", "third")]
```

#5. Create a sequence x from -3:2.
```{r num5}
#output: [1] 1 2 3 4 5 6
sequence <- seq(-3:2)
sequence
```

#6. Create a data frame for month, price per liter (php) and purchase-quantity (liter). Write the R scripts and its output.
#Create a data frame directly
```{r num6}
diesel <- data.frame(
  Month = c("Jan", "Feb", "March", "Apr", "May", "June"),
  Price_Per_Liter = c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00),
  Purchase_quantity = c(25, 30, 40, 50, 10, 45)
)
diesel

#Calculate the weighted mean of fuel expenditure
average_expenditure<- weighted.mean(diesel$Price_Per_Liter, diesel$Purchase_quantity)                                    

#print the average expenditure
average_expenditure
```

#7. Create a vector data with 7 elements
```{r num7}
data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers),
           sd(rivers), min(rivers), max(rivers))
data                 

# The results are: [1]    141.0000  83357.0000    591.1844    425.0000 243908.4086
#[6]    493.8708    135.0000   3710.0000
```

#8. Create vectors according to the table.
```{r num 8a}
#a. Vectors using the data in the table.
power_ranking <- c(1:25)
celeb <- c("Tom Cruise", "Rolling Stone", "Oprah Winfrey", "U2", "Tiger Woods", "Steven Spielberg", "Howard Stern", "50 Cent", "Cast of the Sopranos", "Dan Brown", "Bruce Springsteen", "Donald Trump", "Muhammad Ali", "Paul McCartney", "George Lucas", "Elton John", "David Letterman", "Phil Mickelson", "J.K Rowling", "Brad Pritt", "Peter Jackson", "Dr. Phil McGraw", "Jay Lenon", "Celine Dion", "Kobe Bryant")
power_ranking <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25)
annual_pay <- c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55, 40, 233, 34, 40, 47, 75, 25, 39, 45, 32, 40, 41)
PowerRanking <- data.frame(power_ranking, celeb, annual_pay)
PowerRanking
```

# b. Modify the power ranking and pay of J.K Rowling. Change ppower ranking to 15 and pay to 90.
```{r num8b}
power_ranking[19] <- 15
power_ranking
annual_pay[19] <- 90
annual_pay
```


# c. Create an excel file from the table above and save it as csv file(PowerRanking). Import the csv file into the RStudio
```{r num 8c}
library(readr)
forbesmagazine <- read_csv("forbesmagazine.csv", show_col_types = FALSE)
forbesmagazine
```

```{r 8d}
subset_data <- PowerRanking[10:20, ]
save(subset_data, file = "Ranks.RData")
print (subset_data)
```
# 9
```{r num9a}
library(readxl)
hotels_vienna <- read_excel("hotels-vienna.xlsx")
hotels_vienna
```


```{r num9b}
dimensions <- dim((hotels_vienna))
dimensions
```

```{r num9c}
selected_columns <- hotels_vienna [, c("country", "neighbourhood", "price", "stars", "accommodation_type", "rating")]
head(selected_columns, n = nrow(selected_columns))
```

```{r num9d}
save(selected_columns, file = "new.RData")
```

```{r num9e}
load("new.RData")
head(selected_columns)
tail(selected_columns)
```

# 10
```{r num10a}
Vegetables <- list("cabbage", "carrots", "potato", "squash", "eggplant", "okra", "corn", "cucumber", "lettuce", "broccoli")
Vegetables
```



```{r num10b}
vegetableslist <- append(Vegetables, c("cauliflower", "string beans"), after=10)
vegetableslist
```


```{r num10c}
Veggie <- append(vegetableslist, c("papaya", "onion", "garlic", "pechay", "sayote"),after=5)
Veggie
```

```{r num10d}
NewVeggie <- Veggie[c(-5,-10,-15)]
NewVeggie

length(NewVeggie)
```
